Dissertation

### 2023-11-14 Manuscript/manuscript.qmd
partial fix

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
toc: false
toc-depth: 3
toc-location: body
# execute: 
#   warning: false
#   include: true
---

>>>>

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
toc: false
toc-depth: 3
toc-location: body
execute: 
  warning: false
  include: true
---
